Magnetic propeties of a two dimentional electron gas strongly coupled to lights

### 2021-04-09 theory/sec_02.tex
Add scattering probability

\noindent
First subtitute a general electron state $\Psi(\vb{r},t)$ at time $t$ as the incoming electron to the Schrodinger equation given in Eq. \eqref{2.1}
\begin{equation} \label{2.5}
  i \hbar \pdv{t} \sum_j a_j(t) \ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
\begin{equation} \label{2.6}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} + a_j(t)\pdv{t}\ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
since all the ${\ket{\psi(t)}}$ staistfy the Schrodinger equation \eqref{1.18}
\begin{equation} \label{2.7}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} = \sum_j U(\vb{r}) a_j(t) \ket{\psi_j(t)}.
\end{equation}
Then take inner product with state with the state $\ket{\psi_{j'}(t)}$
\begin{equation} \label{2.8}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} = \sum_j
  a_j(t) \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
But using the \textit{Born approximation} we can assume that this incoming wave have the initial state of the electron at $t=0$ and therefore this equation will modified to
\begin{equation} \label{2.9}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
due to orthonormality this becomes
\begin{equation} \label{2.10}
  i \hbar \dot{a_{j'}}(t) =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
and finally this leads to first order pertubation theory for Sscattering as follows
\begin{equation} \label{2.11}
   \dot{a_{j'}}(t) =
  -\frac{i}{\hbar}\bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
where
\begin{equation} \label{2.12}
   a_{j'}(t) =
  -\frac{i}{\hbar}
  \int_0^t dt' \int_S d\vb{r} \;
  \psi_{j'}^{*} (\vb{r},t') U(\vb{r}) {\psi_j(\vb{r},t')}
\end{equation}
where the integration should be performed over the 2DEG area $S=L_xL_y$. Then we can calculate this using the eqution we derived in \eqref{1.52} as follows
\begin{equation} \label{2.13}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big) \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
    & \times
    U(\vb{r}) \\
    & \times
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
    \bigg]
  \end{aligned}
\end{equation}
then this will be simplified to
\begin{equation} \label{2.14}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big)
   U(\vb{r})
   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big)  \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
    \bigg]
  \end{aligned}
\end{equation}

>>>>

\noindent
First subtitute a general electron state $\Psi(\vb{r},t)$ at time $t$ as the incoming electron to the Schrodinger equation given in Eq. \eqref{2.1}
\begin{equation} \label{2.5}
  i \hbar \pdv{t} \sum_j a_j(t) \ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
\begin{equation} \label{2.6}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} + a_j(t)\pdv{t}\ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
since all the ${\ket{\psi(t)}}$ staistfy the Schrodinger equation \eqref{1.18}
\begin{equation} \label{2.7}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} = \sum_j U(\vb{r}) a_j(t) \ket{\psi_j(t)}.
\end{equation}
Then take inner product with state with the state $\ket{\psi_{j'}(t)}$
\begin{equation} \label{2.8}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} = \sum_j
  a_j(t) \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
But using the \textit{Born approximation} we can assume that this incoming wave have the initial state of the electron at $t=0$ and therefore this equation will modified to
\begin{equation} \label{2.9}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
due to orthonormality this becomes
\begin{equation} \label{2.10}
  i \hbar \dot{a_{j'}}(t) =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
and finally this leads to first order pertubation theory for Sscattering as follows
\begin{equation} \label{2.11}
   \dot{a_{j'}}(t) =
  -\frac{i}{\hbar}\bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
where
\begin{equation} \label{2.12}
   a_{j'}(t) =
  -\frac{i}{\hbar}
  \int_0^t dt' \int_S d\vb{r} \;
  \psi_{j'}^{*} (\vb{r},t') U(\vb{r}) {\psi_j(\vb{r},t')}
\end{equation}
where the integration should be performed over the 2DEG area $S=L_xL_y$. Then we can calculate this using the eqution we derived in \eqref{1.52} as follows
\begin{equation} \label{2.13}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big) \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[E_{n'}t' - m'\frac{2\pi \hbar x}{L_x} -
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t')-
   m_e\dot{\zeta}(t)\big[y - {y'}_0 -\zeta(t')\big]
    - \int_0^{t'}dt'L(\zeta,\dot{\zeta},t")\bigg]) \\
    & \times
    U(\vb{r}) \\
    & \times
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ - E_{n}t' + m\frac{2\pi \hbar x}{L_x} -
    \frac{eE(y-y_0)}{\omega}\cos(\omega t') -
    m_e\dot{\zeta}(t')\big[y - y_0 -\zeta(t')\big]
     - \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg])
    \bigg]
  \end{aligned}
\end{equation}
then this will be simplified to
\begin{equation} \label{2.14}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
   U(\vb{r})
   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)  \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[ E_{n'}t' - m'\frac{2\pi \hbar x}{L_x} -
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t') -
   m_e\dot{\zeta}(t')\big[y - {y'}_0 -\zeta(t')\big]
    - \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg]) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ - E_{n}t' + m\frac{2\pi \hbar x}{L_x} +
    \frac{eE(y-y_0)}{\omega}\cos(\omega t') +
    m_e\dot{\zeta}(t')\big[y - y_0 -\zeta(t')\big]
     + \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg])
    \bigg]
  \end{aligned}
\end{equation}
\begin{equation} \label{2.15}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
   U(\vb{r})
   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)
   \exp(\frac{2\pi i(m-m') \hbar x}{L_x})
   \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[ E_{n'}t' +
   \frac{eE{y'}_0}{\omega}\cos(\omega t') +
   m_e\dot{\zeta}(t'){y'}_0
    \bigg])
      \exp(
     \frac{i}{\hbar}\bigg[ - E_{n}t' -
    \frac{eEy_0}{\omega}\cos(\omega t') -
    m_e\dot{\zeta}(t)y_0
    \bigg])
    \bigg].
  \end{aligned}
\end{equation}
The time dependence of the $chi_n(y)$ can neglect since it is integrate over all the values of the $y$ and we can write this as
\begin{equation} \label{2.16}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_S d\vb{r} \;
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
   U(\vb{r})
   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)
   \exp(\frac{2\pi i(m-m') \hbar x}{L_x})
   \\ & \times
   \int_0^t dt' \;
   \bigg[
     \exp(
    \frac{i}{\hbar}\bigg[ (E_{n'} -E_{n}) t' +
   \frac{eE({y'}_0 - y_0)\omega_0^2}{\omega(\omega_0^2-\omega^2)}\cos(\omega t')
    \bigg])
    \bigg].
  \end{aligned}
\end{equation}
Using Jacobi-Anger expansion
\begin{equation} \label{2.17}
  e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_j(z)e^{in\theta}
\end{equation}
above eqution can be modified as
\begin{equation} \label{2.18}
  \begin{aligned}
    a_{j'}(t)  =
   -\frac{i}{\hbar}
   U_{j'j}
   \int_0^t dt' \;
   \bigg[
   \sum_{l=-\infty}^{\infty} i^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \exp(
    \frac{i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
    \bigg]
  \end{aligned}
\end{equation}
where
\begin{equation} \label{2.19}
  U{j'j} \equiv \mel{\Phi_{j'}(\vb{r})}{U(\vb{r})}{\Phi_j(\vb{r})}
\end{equation}
with bare electron eigen states (without dressing field)
\begin{equation} \label{2.20}
  \Phi_{j}(\vb{r}) = \frac{1}{\sqrt{L_x}}\exp(\frac{2\pi im \hbar x}{L_x}) \chi_{n}(y).
\end{equation}
Considering time evalution from negative values we can write the same expression as follows
\begin{equation} \label{2.21}
  \begin{aligned}
    a_{j'}(t)  =
   -\frac{i}{\hbar}
   U_{j'j}
   \int_{-t/2}^{t/2} dt' \;
   \bigg[
   \sum_{l=-\infty}^{\infty} i^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \exp(
    \frac{i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
    \bigg].
  \end{aligned}
\end{equation}
To calculate scattering probability we can use this scattering amplitude's squre value
\begin{equation} \label{2.22}
  \begin{aligned}
    |a_{j'}(t)|^2  =
   \frac{|U_{j'j}|^2}{\hbar^2} &
   \int_{-t/2}^{t/2} dt' \;
   \bigg[
   \sum_{l=-\infty}^{\infty} {-i}^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \exp(
    \frac{-i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
    \bigg] \\
    & \times
    \int_{-t/2}^{t/2} dt^{''} \;
    \bigg[
    \sum_{k=-\infty}^{\infty} i^k J_k\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
      \exp(
     \frac{i}{\hbar} (E_{n'} -E_{n} + k\hbar\omega) t^{''})
     \bigg]
  \end{aligned}
\end{equation}
Considering long time $t\rightarrow \infty$ we can make the integral into a delta function as follows
\begin{equation} \label{2.22}
  \begin{aligned}
    |a_{j'}(t)|^2  =
   4\pi^2|U_{j'j}|^2 &
   \bigg[
   \sum_{l=-\infty}^{\infty} {-i}^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \delta(-E_{n'} +E_{n} - l\hbar\omega)
     \bigg] \\
    & \times
    \bigg[
    \sum_{k=-\infty}^{\infty} i^k J_k\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
      \delta(E_{n'} - E_{n} + k\hbar\omega)
     \bigg]
  \end{aligned}
\end{equation}
and this implies $l=k$ and this leads to
\begin{equation} \label{2.22}
  \begin{aligned}
    |a_{j'}(t)|^2  =
   4\pi^2|U_{j'j}|^2
   \bigg[
   \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \delta^2(E_{n'} - E_{n} + l\hbar\omega).
  \end{aligned}
\end{equation}
Then using the famous the square $\delta$ function transormation method
\begin{equation} \label{2.22}
  \begin{aligned}
     \delta^2(\epsilon ) = \delta(\epsilon )\delta^2(0)
     \lim_{t\rightarrow\infty} \int_{-t/2}^{t/2} e^{i0\times t' /\hbar} dt' =
     \frac{\delta(\epsilon) t}{2\pi \hbar}
  \end{aligned}
\end{equation}
we can calculatre the probability of electron scattering between states $j$ and $j'$ per unit time as
\begin{equation} \label{2.22}
    \mathcal{W}_{j'j} \equiv \dv{|a_{j'}(t)|^2}{t} =
    |U_{j'j}|^2 \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
    \times
    \frac{2\pi}{\hbar} \delta(E_{n'} - E_{n} + l\hbar\omega)
\end{equation}
